---
title: "Book Reviews 3"
author: "Amelia Rudberg"
date: "2023-01-13"
output: html_document
---

### Prepping the data  
**Start by loading the tidyverse library**
```{r, message = FALSE}
library(tidyverse)
```

**Then read the csv**
```{r}
book_reviews<-read_csv("book_reviews.csv")
```

### Summarizing the data 

```{r}
dim(book_reviews)
```

There are 2000 rows and 4 columns in this data table. 
```{r}
col_names<-colnames(book_reviews)
```
The columns represent the book name, the review it received, the state it was sold in, and the price of the book.   
  
Next look at the type of each column 
```{r}
for (c in col_names){
  print(typeof(book_reviews[[c]]))
}
```
```{r}
for (c in col_names){
  print("Unique Values in Column:")
  print(c)
  print(unique(book_reviews[[c]]))
  print("")
}
```

### Cleaning the data   
***Remove missing data***
As we can see in the unique values output, review is the only column with missing data. 

```{r}
complete_book_reviews<-book_reviews %>% filter(!is.na(review))
dim(complete_book_reviews)
```
Slightly more than 200 rows were removed due to a missing review. 

***Standardize Names***
```{r}
complete_book_reviews <- complete_book_reviews %>% mutate(
  state= case_when(
  state == "California" ~ "CA", 
  state ==  "New York" ~ "NY", 
  state == "Florida" ~ "FL", 
  state == "Texas" ~ "TX",
  TRUE ~ state
)
)
```

***Convert Ratings to Numbers***  
```{r}
complete_book_reviews<-complete_book_reviews %>% mutate(
  review_num = case_when(
    review == "Poor" ~ 1, 
    review == "Fair" ~ 2, 
    review == "Good" ~ 3, 
    review == "Great" ~ 4, 
    review == "Excellent" ~ 5
  ),
  is_high_review = if_else(review_num >= 4, TRUE, FALSE)
  )
```

*** Calculate the Most Profitable Book***
Next we will create a summary table with the number of books sold, the purchase price, and the total revenue for each book. When we sort this in descending order of 
```{r}
books_total<- complete_book_reviews %>% group_by(book) %>% summarize(
  purchased = n(),
  price = mean(price)
) %>% mutate(
  revenue = purchased*price
) %>% arrange(-revenue)
```

***Based on these calculations, we can see "Secrets Of R For Advanced Students" is the most profitable book***
